A general approach to maximise information density in neutron reflectometry analysis

### 2020-05-11 paper/paper.tex
add zenodo doi

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/model_select} (DOI: 10.5281/zenodo.xxxxxxx) under a CC BY-SA 4.0 license.

>>>>

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible, and automated, analysis workflow for the work presented is available at \url{https://github.com/arm61/model_select} (DOI: 10.5281/zenodo.3820690) under a CC BY-SA 4.0 license.
